---
title: "Jail Pilot Wide to Long"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Creating Long Dataset

* This is the analysis sample: Cases not used in analyses were dropped.
    * Cases without complete data on predictors were dropped because complete data on predictors is required for analysis.
    * Cases missing all outcomes were dropped. Cases with at least one outcome can be used in analyses.

```{r}
Jail_clean_long <- Jail_clean %>% 
    dplyr::filter(in.analysis.sample == TRUE) %>% 
    dplyr::select(ID, 
                  Age, 
                  `Age (Decades)`,
                  Age_Groups,
                  Ethnic_Code, 
                  Race_Dichotomous,
                  Education_collapsed,
                  Education_3cat,
                  Prior_RshpEducation,
                  Prior_RshpEducation_collapsed,
                  FinancialWorry_cat,
                  Income,
                  `Income (10K)`,
                  Number_Attended,
                  Dosage,
                  Gender,
                  Divorced_Dichotomous,
                  Healthy_Rel_Skills_Change,
                  Partner_Selection_Change,
                  Past_Rel_Behav_Change,
                  Rel_Behav_Attit_Change) %>% 
    tidyr::gather(key = var,
                  value = Change.Score,
                  Healthy_Rel_Skills_Change,
                  Partner_Selection_Change,
                  Past_Rel_Behav_Change,
                  Rel_Behav_Attit_Change) %>% 
    dplyr::mutate_at(vars(ID, var), factor) %>% 
    dplyr::arrange(ID, var) %>% 
    dplyr::mutate(Age_Decades = `Age (Decades)`) %>% 
    dplyr::mutate(Income_10K = `Income (10K)`)
```


```{r}
Jail_clean_long
```

# Creating Long Dataset with all available data on significant predictors

* This is the analysis sample: Cases not used in analyses were dropped.
    * Cases without complete data on significant predictors were dropped because complete data on predictors is required for analysis.
    * Cases missing all outcomes were dropped. Cases with at least one outcome can be used in analyses.

```{r}
Jail_clean_long2 <- Jail_clean %>% 
    dplyr::filter(in.analysis.sample2 == TRUE) %>% 
    dplyr::select(ID, 
                  Age, 
                  `Age (Decades)`,
                  Age_Groups,
                  Ethnic_Code, 
                  Race_Dichotomous,
                  Education_collapsed,
                  Education_3cat,
                  Prior_RshpEducation,
                  Prior_RshpEducation_collapsed,
                  FinancialWorry_cat,
                  Income,
                  `Income (10K)`,
                  Number_Attended,
                  Dosage,
                  Gender,
                  Divorced_Dichotomous,
                  Healthy_Rel_Skills_Change,
                  Partner_Selection_Change,
                  Past_Rel_Behav_Change,
                  Rel_Behav_Attit_Change) %>% 
    tidyr::gather(key = var,
                  value = Change.Score,
                  Healthy_Rel_Skills_Change,
                  Partner_Selection_Change,
                  Past_Rel_Behav_Change,
                  Rel_Behav_Attit_Change) %>% 
    dplyr::mutate_at(vars(ID, var), factor) %>% 
    dplyr::arrange(ID, var) %>% 
    dplyr::mutate(Age_Decades = `Age (Decades)`) %>% 
    dplyr::mutate(Income_10K = `Income (10K)`)
```

```{r}
Jail_clean_long2
```


# Creating Long long Dataset for MLM over TIme

* This is the analysis sample: Cases not used in analyses were dropped.
    * Cases without complete data on predictors were dropped because complete data on predictors is required for analysis.
    * Cases missing all outcomes were dropped. Cases with at least one outcome can be used in analyses.

```{r}
Jail_clean_longlong <- Jail_clean %>% 
    dplyr::filter(in.analysis.sample3 == TRUE) %>% 
    dplyr::rename(Healthy_Rel_SkillsPost = Healthy_Rel_Skills,
                  Partner_SelectionPost = Partner_Selection,
                  Past_Rel_BehavPost = Past_Rel_Behav,
                  Rel_Behav_AttitPost = Rel_Behav_Attit,
                  Healthy_Rel_SkillsRPre = Healthy_Rel_Skills_Before,
                  Partner_SelectionRPre = Partner_Selection_Before,
                  Past_Rel_BehavRPre = Past_Rel_Behav_Before,
                  Rel_Behav_AttitRPre = Rel_Behav_Attit_Before) %>% 
    dplyr::select(ID, 
                  Age, 
                  `Age (Decades)`,
                  Age_Groups,
                  Ethnic_Code, 
                  Race_Dichotomous,
                  Education_3cat,
                  Education_collapsed,
                  Prior_RshpEducation,
                  Prior_RshpEducation_collapsed,
                  FinancialWorry_cat,
                  Income,
                  `Income (10K)`,
                  Number_Attended,
                  Dosage,
                  Gender,
                  Divorced_Dichotomous,
                  Healthy_Rel_SkillsRPre,
                  Partner_SelectionRPre,
                  Past_Rel_BehavRPre,
                  Rel_Behav_AttitRPre,
                  Healthy_Rel_SkillsPost,
                  Partner_SelectionPost,
                  Past_Rel_BehavPost,
                  Rel_Behav_AttitPost) %>% 
    tidyr::gather(key = var,
                  value = Score,
                  Healthy_Rel_SkillsRPre,
                  Partner_SelectionRPre,
                  Past_Rel_BehavRPre,
                  Rel_Behav_AttitRPre,
                  Healthy_Rel_SkillsPost,
                  Partner_SelectionPost,
                  Past_Rel_BehavPost,
                  Rel_Behav_AttitPost) %>% 
    tidyr::separate(col = var, into = c("Domain","Time"), sep = -4) %>%  
    dplyr::mutate_at(vars(ID,Domain, Time), factor) %>% 
    dplyr::arrange(ID, Domain, Time) %>% 
    dplyr::mutate(Time = factor(Time, 
                                levels = c("RPre", "Post"))) %>% 
    dplyr::mutate(Age_Decades = `Age (Decades)`) %>% 
    dplyr::mutate(Income_10K = `Income (10K)`)
```


```{r}
Jail_clean_longlong
```

# Using Collapsed Reasonse Options: Creating Long long Dataset 2 for MLM over TIme

* This is the analysis sample: Cases not used in analyses were dropped.
    * Cases without complete data on predictors were dropped because complete data on predictors is required for analysis.
    * Cases missing all outcomes were dropped. Cases with at least one outcome can be used in analyses.

```{r}
Jail_clean_longlong2 <- Jail_clean %>% 
    dplyr::filter(in.analysis.sample3 == TRUE) %>% 
    dplyr::rename(Healthy_Rel_SkillsPost = Healthy_Rel_Skills.3,
                  Partner_SelectionPost = Partner_Selection.3,
                  Past_Rel_BehavPost = Past_Rel_Behav.3,
                  Rel_Behav_AttitPost = Rel_Behav_Attit.3,
                  Healthy_Rel_SkillsRPre = Healthy_Rel_Skills_Before.3,
                  Partner_SelectionRPre = Partner_Selection_Before.3,
                  Past_Rel_BehavRPre = Past_Rel_Behav_Before.3,
                  Rel_Behav_AttitRPre = Rel_Behav_Attit_Before.3) %>% 
    dplyr::select(ID, 
                  Age, 
                  `Age (Decades)`,
                  Age_Groups,
                  Ethnic_Code, 
                  Race_Dichotomous,
                  Education_collapsed,
                  Education_3cat,
                  Prior_RshpEducation,
                  Prior_RshpEducation_collapsed,
                  FinancialWorry_cat,
                  Income,
                  `Income (10K)`,
                  Number_Attended,
                  Dosage,
                  Gender,
                  Divorced_Dichotomous,
                  Healthy_Rel_SkillsRPre,
                  Partner_SelectionRPre,
                  Past_Rel_BehavRPre,
                  Rel_Behav_AttitRPre,
                  Healthy_Rel_SkillsPost,
                  Partner_SelectionPost,
                  Past_Rel_BehavPost,
                  Rel_Behav_AttitPost) %>% 
    tidyr::gather(key = var,
                  value = Score,
                  Healthy_Rel_SkillsRPre,
                  Partner_SelectionRPre,
                  Past_Rel_BehavRPre,
                  Rel_Behav_AttitRPre,
                  Healthy_Rel_SkillsPost,
                  Partner_SelectionPost,
                  Past_Rel_BehavPost,
                  Rel_Behav_AttitPost) %>% 
    tidyr::separate(col = var, into = c("Domain","Time"), sep = -4) %>%  
    dplyr::mutate_at(vars(ID,Domain, Time), factor) %>% 
    dplyr::arrange(ID, Domain, Time) %>% 
    dplyr::mutate(Time = factor(Time, 
                                levels = c("RPre", "Post"))) %>% 
    dplyr::mutate(Age_Decades = `Age (Decades)`) %>% 
    dplyr::mutate(Income_10K = `Income (10K)`)
```



# Using Collapsed Reasonse Options: Creating Long long Dataset 2 for MLM over TIme

* This is the analysis sample: Cases not used in analyses were dropped.
    * Cases without complete data on predictors were dropped because complete data on predictors is required for analysis.
    * Cases missing all outcomes were dropped. Cases with at least one outcome can be used in analyses.

```{r}
Jail_clean_longlong4 <- Jail_clean %>% 
    dplyr::filter(in.analysis.sample4 == TRUE) %>% 
    dplyr::rename(Healthy_Rel_SkillsPost = Healthy_Rel_Skills.3,
                  Partner_SelectionPost = Partner_Selection.3,
                  Past_Rel_BehavPost = Past_Rel_Behav.3,
                  Rel_Behav_AttitPost = Rel_Behav_Attit.3,
                  Healthy_Rel_SkillsRPre = Healthy_Rel_Skills_Before.3,
                  Partner_SelectionRPre = Partner_Selection_Before.3,
                  Past_Rel_BehavRPre = Past_Rel_Behav_Before.3,
                  Rel_Behav_AttitRPre = Rel_Behav_Attit_Before.3) %>% 
    dplyr::select(ID, 
                  Age, 
                  `Age (Decades)`,
                  Age_Groups,
                  Ethnic_Code, 
                  Race_Dichotomous,
                  Education_collapsed,
                  Education_3cat,
                  Prior_RshpEducation,
                  Prior_RshpEducation_collapsed,
                  FinancialWorry_cat,
                  Income,
                  `Income (10K)`,
                  Number_Attended,
                  Dosage,
                  Gender,
                  Divorced_Dichotomous,
                  Healthy_Rel_SkillsRPre,
                  Partner_SelectionRPre,
                  Past_Rel_BehavRPre,
                  Rel_Behav_AttitRPre,
                  Healthy_Rel_SkillsPost,
                  Partner_SelectionPost,
                  Past_Rel_BehavPost,
                  Rel_Behav_AttitPost) %>% 
    tidyr::gather(key = var,
                  value = Score,
                  Healthy_Rel_SkillsRPre,
                  Partner_SelectionRPre,
                  Past_Rel_BehavRPre,
                  Rel_Behav_AttitRPre,
                  Healthy_Rel_SkillsPost,
                  Partner_SelectionPost,
                  Past_Rel_BehavPost,
                  Rel_Behav_AttitPost) %>% 
    tidyr::separate(col = var, into = c("Domain","Time"), sep = -4) %>%  
    dplyr::mutate_at(vars(ID,Domain, Time), factor) %>% 
    dplyr::arrange(ID, Domain, Time) %>% 
    dplyr::mutate(Time = factor(Time, 
                                levels = c("RPre", "Post"))) %>% 
    dplyr::mutate(Age_Decades = `Age (Decades)`) %>% 
    dplyr::mutate(Income_10K = `Income (10K)`)
```



# Saving data Set
```{r}
save(Jail_clean, file="./Data/Jail_clean.Rda")
save(Jail_clean_long, file="./Data/Jail_clean_long.Rda")
save(Jail_clean_long2, file="./Data/Jail_clean_long2.Rda")
save(Jail_clean_longlong, file="./Data/Jail_clean_longlong.Rda")
save(Jail_clean_longlong2, file="./Data/Jail_clean_longlong2.Rda")
save(Jail_clean_longlong4, file="./Data/Jail_clean_longlong4.Rda")

```





## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
